A pipeline to analyse time-course gene expression data

### 2020-07-21 scripts/manuscript.Rmd
uncomment

```{r genesVsCentroids, fig.height=6, fig.width=6}
cluster_of_interest = 2
cluster2Genes = names(
    kmeans_clusters$clusters[kmeans_clusters$clusters==cluster_of_interest])
# FIXME This line fails
# dataToPlot = rbind(
#     assay(de_moanin_model[cluster2Genes[3:6],]), 
#    "Centroid"=kmeans_clusters$centroids[cluster_of_interest,])
# plot_splines_data(de_moanin_model, data=dataToPlot, 
#     colors=ann_colors$Group, smooth=TRUE, simpleY=FALSE,
#    mar=c(1.5,2.5,2,0.1))
```

@@

```{r topScoreInCluster2, fig.height=6, fig.width=6, fig.cap=paste("Top scoring genes in Cluster",cluster_of_interest)}
# order them by their score in cluster
ord = order(scores_and_labels$scores[genes_in_cluster2,
                     cluster_of_interest])
cluster2Score = genes_in_cluster2[ord]
# FIXME this lines failes.
# dataToPlot = rbind(assay(moanin_model[cluster2Score[1:4], ]),
#     "Centroid"=kmeans_clusters$centroids[cluster_of_interest, ])
# plot_splines_data(moanin_model, data=dataToPlot, 
#     colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
#     mar=c(1.5,2.5,2,0.1))
```

@@

# Now use the results of the previous call to aheatmap to reorder the genes.
# FIXME this line doesn't work
# aheatmap(
#    rescale_values(moanin_model[genes_to_plot,ord])[res$rowInd,],
#    Colv=NA,
#    Rowv=NA,
#    annCol=orderedMeta[, c("Group", "Timepoint")],
#    annLegend=TRUE,
#    annColors=ann_colors,
#    main=paste("Cluster", cluster_to_plot, "(rescaled)"),
#    treeheight=0)

>>>>

```{r genesVsCentroids, fig.height=6, fig.width=6}
cluster_of_interest = 2
cluster2Genes = names(
    kmeans_clusters$clusters[kmeans_clusters$clusters==cluster_of_interest])
# FIXME This line fails
dataToPlot = rbind(
     assay(de_moanin_model[cluster2Genes[3:6],]), 
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest,])
plot_splines_data(de_moanin_model, data=dataToPlot, 
     colors=ann_colors$Group, smooth=TRUE, simpleY=FALSE,
    mar=c(1.5,2.5,2,0.1))
```

@@

```{r topScoreInCluster2, fig.height=6, fig.width=6, fig.cap=paste("Top scoring genes in Cluster",cluster_of_interest)}
# order them by their score in cluster
ord = order(scores_and_labels$scores[genes_in_cluster2,
                     cluster_of_interest])
cluster2Score = genes_in_cluster2[ord]
# FIXME this lines failes.
dataToPlot = rbind(assay(moanin_model[cluster2Score[1:4], ]),
     "Centroid"=kmeans_clusters$centroids[cluster_of_interest, ])
plot_splines_data(moanin_model, data=dataToPlot, 
     colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
     mar=c(1.5,2.5,2,0.1))
```

@@

# Now use the results of the previous call to aheatmap to reorder the genes.
# FIXME this line doesn't work
aheatmap(
   rescale_values(moanin_model[genes_to_plot,ord])[res$rowInd,],
   Colv=NA,
   Rowv=NA,
   annCol=orderedMeta[, c("Group", "Timepoint")],
   annLegend=TRUE,
   annColors=ann_colors,
   main=paste("Cluster", cluster_to_plot, "(rescaled)"),
   treeheight=0)
